A finite-state morphological transducer for Kyrgyz

### 2012-03-21 paper/paper.tex
punctuation commas semicolons and bears oh my

Low recall is due to forms which do not receive any analyses, in all cases this was due to missing stems in the lexicon. Out of the 1,000 words, 91 did not receive any analyses. Of these, 52 forms were proper names 28 were nouns, 6 were adjectives and the remaining 5 verbs.  This would suggest that in terms of adding new stems, it would be a good idea to look at increasing both the number of proper names, and nouns.

>>>>

Low recall is due to forms which do not receive any analyses; in all cases this was due to stems missing in the lexicon. Out of the 1,000 words, 91 did not receive any analyses. Of these, 52 forms were proper names, 28 were nouns, 6 were adjectives, and the remaining 5 verbs.  This would suggest that in terms of adding new stems, it would be a good idea to look at increasing both the number of proper names and nouns.
